---
title: "simul_results"
output: html_document
runtime: shiny
---
```{r include=F}
library(shiny)
library(widgetframe)
```

### N-mixture model performance and optimal survey design

Choose a scenario of local abundance in sites $\lambda$ and individual availability probability $\phi$ to see single and double observer models performance (relative RMSE curves) and optimal survey effort allocation (optimal number of visits).

\ 
<iframe height="1500" width="110%" frameborder="no" 
src="https://ismaelbrack.shinyapps.io/simulNmix_results/"> </iframe>
\ 
\ 

### Improving accuracy in abundance estimation by using a double-observer protocol

Increase in model accuracy by using a double-observer protocol when compared to a single observer model (as a baseline).

```{r, ,echo=F, out.width='75%', fig.align='center',fig.cap="Figure: xxx"}
knitr::include_graphics('xxx')
```

\ 
### Reducing fieldwork effort with double observer review

Proportional reduction in fieldwork effort (from $B=2000$ flights) that can be achieved with a full double-observer protocol, while matching the same accuracy of the single observer model (for $p=0.8$).

```{r, ,echo=F, out.width='75%', fig.align='center'}
knitr::include_graphics('xxx')
```

\  
\  
<font size="2"> 
For more details on the simulation methods and results check out the original paper. 
</font>


